Weed and Corn segmentation through Convolutional Neuronal Networks

### 2017-05-19 PaperBCJ.tex

\section{Matherial and Methods}
%Codigo para la Implementacion del Algoritmo

\begin{figure}
  \centering

  \caption{Some figure}
\end{figure}

@@

>>>>

\section{Matherial and Methods}
%Codigo para la Implementacion del Algoritmo
The development of the model for the weed and maize detection algorithm using convolutional neural networks is described below.
\\
\subsection{Hardward}
The card used is a Raspberry Pi 3. The camera used for both the sampling and the model was a RaspBerry Pi Camera module v2, 		which is configured to obtain a video at a resolution of 640 by 480 pixels , In order to improve the performance of image 	processing.
\\

\subsection{Software}

The programs / packages used were OpenCV and Qt, for the acquisition, segmentation of images, Cafe for the realization of neural networks,
\\
\subsection{Neural networks}
For the training of neural networks we used an AlexNet architecture, but we do quizes with others architectures like Let Net, Inception Ned, but the results wont good.
\\
\subsection{Dataset Desciption}
	\begin{figure}[!t]
	For the model we have two categories, the first maize in its initial stage, and the second weed, All images for the dataset were obtained from maize cultivations in their initial stage in Pillaro canton, where they had a total of  2225 images, of which 1622 images were of maize and 603 of weed, once obtained the images are processed by openCV to segment them and can be obtained as follows:
	\\

	\centering
	\includegraphics[width=2.5in]{im1}
	\caption{Simulation results for the network.}
	\label{fig_sim}

@@

\end{figure}
